---
title: "Regression Models Course Project"
output: html_document
date: "21 de diciembre de 2014"
---

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

“Is an automatic or manual transmission better for MPG”
"Quantify the MPG difference between automatic and manual transmissions"


### Loading data

```{r}
data(mtcars)
transmissionData <- factor(mtcars$am, labels = c("automatic", "manual"))
summary(transmissionData)
```


### Data Visualization

Using the mtcars data we make a plot to see the the relationship between mpg variable and transmission type variable (am).

```{r}
library(ggplot2)

p <- ggplot(mtcars, aes(factor(transmissionData), mpg))
p <- p + geom_boxplot(aes(fill=factor(transmissionData)))
p <- p + ggtitle('MPG vs Transmission Type')
p <- p + labs(x='Transmission Type', y='Miles per Gallon')

print(p)

```

In the graphic above, it is shown that the transmission type have a significant impact on MPG variable, so it appears that the manual transmission is better than the automatic.

### Data Analysis

Mean test to determine whether the means of two groups are equal to each other.

```{r}
t.test(mpg~am, data=mtcars)
```

The p-value is low so we can reject the null hypothesis so the manual transmission seems to be better for the mpg variable.

### Regression

```{r}
reg_model_01 <- lm(mpg~am, data = mtcars)
summary(reg_model_01)$coef
```

### Results

The regression coefficient can be interpreted as follows: if we only use am (transmission type) as predictor, cars with manual transmissions have mpg values 7.2 higher than those cars with the automatic transmissions. 

